### 2014-03-12 src/introduction.Rnw
update

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It involves producing
a family of mutants with simple differences from the original program, and evaluating the
effectiveness of test-suites against the these mutants~\cite{lipton1971fault, ammann2008introduction}.
Previous research~\cite{andrews2005mutation} suggests that mutations thus introduced behave
in a fashion similar to the real-faults with respect to the difficulty of detection.

@@

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field has a serious lacuna in
large scale research, both in the size of the programs studied, and in the number and diversity
of programs, which reduces our confidence in the espoused results. This is true both for
selective mutation, sampling strategies, and also for comparatively newer studies that attempt
to join them together.  This is particularly worrisome if mutation analysis is to gain wider
acceptance among testing professionals. Further quite a few of the influential studies has been
conducted on older programming languages such as Fortran with operators specific to it, which
may not carry over to the newer and popular languages such as Java. Finally, with the modern
research into the ``do-smarter'' approach which allows byte code based mutation -- thus eliminating
the compilation step -- operators based on source code modification is no longer be applicable, and
their equivalents in the bytecode needs to be found and compared with other approaches. A detailed
discussion of these issues can be found in Section~\ref{sec:related}.

% RAHUL>AMIN: I find the non-bulleted contributions better flowing as I can work the references
% to other sections into it. Let me know if you have a better idea (As it stands neither my
% previous wording, nor your bulleted list reads good)
We have attempted to rectify this situation with a large scale study of industrial programs.
As detailed in Section~\ref{sec:methodology}, we sample 188 real world Java programs from Github, with
size ranging from 50loc to 100kloc, which makes our inferences relatively strong, and widely applicable.
We provide the results from running both original human generated test-suites, and also programmatically
generated test-suites, increasing the applicability of our findings to both researchers who seek to
compare test-suites quickly, and to industrial software testers who might be looking for a way to reduce
the time of their build cycle when using mutation coverage. The Section~\ref{sec:methodology} discusses
the sampling strategies attempted, and the operator selection strategies in detail, and the results of
our experiment are given in Section~\ref{sec:results}, followed by detailed discussion of what it implies
in section ~\ref{sec:discussion}. The research concludes in Section~\ref{sec:conclusion}.

@@

\begin{itemize}
\item Our study is the largest so far in terms of both the size of programs involved, and the number of
  programs analyzed for ``do-fewer'' strategies, which makes our inferences stronger and widely applicable.
\item We compare a large number of ``do-fewer'' strategies, especially with respect to their predictive
  power over the final mutation score.
\item Our sampling strategies include some that were suggested by other researchers, and also a few novel
  strategies that has not been published elsewhere.
\item Our recommendations are valid for both testing researchers who might be comparing programmatically
  generated test-suites, and software testing professionals working on real test-suites.
\end{itemize}

\begin{itemize}
\item Extensive study using 188 unique projects. % comparing to Zhang's 12 projects
\item Various sampling techniques.  % currently we have 24*4 sampling comparing to 6*4 in Zhang's  
\item simpler schemes work better. %Don't try sophisticated schemes. against Zhang's impression future work.
\item Sampling at coarsest level (i.e. project level) gives the best result. % against Zhang's findings
\item Single line sampling gives better results than statement deletion. % comparing random selection and operator selection.
 % SDL has been recommended by Offutt.

>>>>

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It
involves producing a family of mutants with simple differences from the
original program, and evaluating the effectiveness of test-suites against
these mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus introduced
behave in a fashion similar to the real-faults with respect to the difficulty
of detection.

@@

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
field has a serious lacuna in large scale research, both in the
size of the programs studied, and in the number and diversity of
programs, which reduces our confidence in their results. This is
true for selective mutation studies, studies in sampling, and also
for comparatively newer studies that attempt to combine them. This is
particularly worrisome if mutation analysis is to gain wider acceptance
among testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing}
has been conducted on older programming languages such as Fortran with
operators specific to it, and are not directly applicable to newer languages
such as Java, with significant differences. Finally, with the modern research
into the ``do-smarter'' approach using byte code based mutation -- eliminating
the compilation step -- operators based on source code modification is no
longer be applicable, and their equivalents in the bytecode needs to be
found and compared with other approaches. A detailed discussion of these
issues can be found in Section~\ref{sec:related}.

% RAHUL>AMIN: I find the non-bulleted contributions better flowing as I can work the references
% to other sections into it. Let me know if you have a better idea (As it stands neither my
% previous wording, nor your bulleted list reads good)
We have attempted to rectify this situation with a large scale study
of industrial programs.  As detailed in Section~\ref{sec:methodology},
we sample 188 real world Java programs from Github, with size ranging
from 50loc to 100kloc, which allows us to make widely applicable
statistical inferences. We provide the results from running both original human
generated test-suites, and also programmatically generated test-suites,
increasing the applicability of our findings to both researchers who seek to
compare test-suites quickly, and to industrial software testers who might be
looking for a way to reduce the time of their build cycle when using mutation
coverage. The Section~\ref{sec:methodology} discusses the sampling strategies
attempted, and the operator selection strategies in detail, and the results of
our experiment are given in Section~\ref{sec:results}, followed by detailed
discussion of what it implies in section ~\ref{sec:discussion}. The research
concludes in Section~\ref{sec:conclusion}.

@@

\begin{itemize}
\item Our study is the largest so far in terms of both the size of programs
involved (50loc to 100kloc), and the number of programs analyzed
(188 unique open source projects) for mutant reduction strategies. This allows
for stronger and widely applicable statistical inferences to be drawn.
\item We compare a much large number of mutant reduction strategies, especially
with respect to their predictive power over the final mutation score, the
expected mutant reduction, and the stability of the amount of mutant reduction
expected. Our sampling strategies include some that were suggested by other
researchers, and also a few novel strategies that has not been published elsewhere.
\item Our recommendations are valid for both testing researchers who might be
comparing programmatically generated test-suites, and software testing
professionals working on real test-suites.
\item Most importanly, we find that the simplest strategy of mutation reduction,
that of x\% sampling is better than more sophesticated strategies in predicting
the final mutation score. This is true not only for those strategies that we
analyzed but also for any other strategies that seek to predict the full mutation
score by looking at only a subset of mutants, irrespective of the kind of
reduction used (operator selection, sampling or clustering, or any other).
\end{itemize}

\begin{itemize}
\item simpler schemes work better. %Don't try sophisticated schemes. against Zhang's impression future work.
\item Sampling at coarsest level (i.e. project level) gives the best result. % against Zhang's findings
\item Single line sampling gives better results than statement deletion. % comparing random selection and operator selection.
 % SDL has been recommended by Offutt.
